Very long and verbose title

### 2022-03-25 docs/holodeck-paper/src/ms.tex
MS: manuscript updates

\newcommand{\thardf}{\tau_f}

@@

        Utimately we are interested in a total number of binaries $N$ such that $dN \equiv n \, dV_c$ for a comoving volume $V_c(z)$.  To find the number of binaries, we use the chain rule to connect the time-evolution of the universe with the evolution of each binary over frequency,
        \begin{equation}
            \diffp{N}{{M}{q}{z}{\ln\!f_r}} = \diffp{n}{{M}{q}{z}} \diffp{z}{t} \diffp{t}{ {\ln\!f_r} } \diffp{V_c}{z}.
        \end{equation}
        Putting this together, we can finally write,
        \begin{equation}
            \diffp{N}{{M}{q}{z}{\ln\!f_r}} = - \Phi(M,z) \, F(M,a,z) \frac{\thardf}{\tau(M,a,z|a')} \diffp{V_c}{z}.
        \end{equation}

@@

>>>>

\newcommand{\thardf}{\tau_f}
\newcommand{\holodeck}{\texttt{holodeck}}
\newcommand{\python}{\texttt{python}}
\newcommand{\mmbulge}{{$M_\textrm{BH}$--$M_\textrm{bulge}$}}

@@

        Utimately we are interested in a total number of binaries $N$ such that $dN \equiv n \, dV_c$ for a comoving volume $V_c(z)$.  To find the number of binaries, we use the chain rule to connect the time-evolution of the universe with the evolution of each binary over frequency,
        \begin{equation}
            \diffp{N}{{M}{q}{z}{\ln\!f_r}} = \diffp{n}{{M}{q}{z}} \diffp{z}{t} \diffp{t}{ {\ln\!f_r} } \diffp{V_c}{z}.
        \end{equation}
        Putting this together, we can finally write,
        \begin{equation}
            \label{eq:sam_final}
            \diffp{N}{{M}{q}{z}{\ln\!f_r}} = - \Phi(M,z) \, F(M,a,z) \frac{\thardf}{\tau(M,a,z|a')} \diffp{V_c}{z}.
        \end{equation}

@@

\section{Implementation}
    \label{sec:imp}

    The \holodeck{} framework is written primarily in \python{} using a class-based structure for modularity and extensibility.

    \subsection{Semi-Analytic Models}
        \label{sec:imp_sam}

        The core of the semi-analytic modeling framework in \holodeck{} is implementing \eqref{eq:sam_final}.  There are classes for each of the key components: The galaxy stellar-mass function (GSMF, $\Phi$), the galaxy pair fraction ($F$), the merger timescale ($\tau$), and additional a scaling relation for mapping host galaxies via to MBH properties --- typically via an \mmbulge{} relation.  Each component class is implemented generically via basic API methods (e.g.~a GSMF that returns the number density of galaxies at a given stellar-mass and redshift), and can be subclassed to provide a particular implementation (e.g.~an analytic Schechter-function GSMF).  The number (or number density) of binaries is specified over a grid of parameters, typically in a four dimensional space of total mass ($M$), mass ratio ($q$), redshift ($z$), and binary rest-frame orbital frequency ($f_r$).

        The semi-analytic model formalism defines a continuous distribution of MBH binaries.  For many calculations, the discrete nature of MBHB sources is important, not only for examining individual continuous wave sources but also because of the important effects of discrete sources on the shape of the GWB due to the non-linear scaling of GW strain \citep{Sesana+2008}.  Additional, a component of the uncertainty in expected GW signals is due to `cosmic variance', which can be treated as Poisson noise when creating multiple samples (or `realizations') of our binary populations.  To handle discretization and resampling we use the \kalepy{} package \citep{kalepy2021}, in particular, a method of outlier sampling to capture regions of parameter space where finite number effects are important.  The \holodeck{} semi-analytic models specify the number (or number-density) of binaries over a grid, i.e.~$N_{ijkl}$.  By definition, grid cells which have an expected total number of binaries $\gg 1$ will not produce appreciable finite-number effects, so instead they are given a weighting based on a Poisson distribution centered around their expectation value, i.e.~$\mathcal{P}(N_{ijkl})$.  Grid cells with expected numbers of order unity or less do produce important finite-number effects, and thus are directly resampled
